---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  echo = TRUE,
  cache = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

# Installation

```
install.packages('devtools') # install devtools if needed
devtools::install_github("dantonnoriega/sppedr") # install the package
```

# Package Datasets

The package, when loaded, also attaches the following datasets. These data sets can be called directly once you have loaded `library(sppedr)`.

```{r data-sppedr, warning=FALSE, message=FALSE, echo=FALSE, eval=TRUE}
code
```


## Example: `cps_address` dataset

```{r cps_address, warning=FALSE, message=FALSE, echo=TRUE, eval=TRUE}
cps_address
```

# Functions

The following functions, in order of usefulness, are available:



## Example: Extracting and combining data from July 14 - 16, 2016

```{r example, warning=FALSE, message=FALSE, echo=TRUE, eval=TRUE}

library(sppedr)
library(magrittr) # for piping %>%

```

This can also be done in a single pipe.

```{r onepipe, warning=FALSE, message=FALSE, echo=TRUE, eval=FALSE}


```

# Other Info

In the [package directory `data-raw`](https://github.com/dantonnoriega/sppedr/tree/master/data-raw), there is a `README.txt` file that explains where all the internal datasets come from and/or how they are built. Scripts that build most of these data are also in `data-raw`. Note that this directory is accessible via the github repo, not the package itself.

