---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  echo = TRUE,
  cache = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

# Installation

```
install.packages('devtools') # install devtools if needed
devtools::install_github("dantonnoriega/sppedr") # install the package
```

# Prerequisites

This package assumes you have access to a directory with the following files and structure

```
spped
└── Data
    ├── cps_2008_2016.dta
    ├── cps_address_2008_2016.dta
    RawData
    ├── CPS_Personnel
    ├── Chicago_Crime
    ├── Crosswalks
    ├── ISBE_Directories
    └── ISBE_School_Data
```

The directory `spped` is considered the data "main directory" (or `main_dir`) by the package. Wherever this is located on your computer, ensure the package knows where it is by running the `set_main_dir()` command.

```{r main-dir, warning=FALSE, message=FALSE, echo=FALSE, eval=TRUE}
library(sppedr)

clear_main_dir() # clear any existing main_dir
try(get_main_dir()) # no main dir
set_main_dir("/Users/danton/Dropbox/ra-work/spped")
# set_main_dir() # can also run without path and it will prompt
get_main_dir()
```

This will allow you to run the package functions from scratch should you want to generate new data.

# Package Datasets

The package, when loaded, also attaches the following datasets. These data sets can be called directly once you have loaded `library(sppedr)`.

```{r data-sppedr, warning=FALSE, message=FALSE, echo=FALSE, eval=TRUE}
library(sppedr)
data(package = 'sppedr') # list of all available data
```

## Dataset Descriptions

- `cps_2008_2016`: school data for years 2008 to 2016. this is a csv version of the dta file `cps_2008_2016.dta`
- `cps_school_year`: this contains dates about the academic school year. it is a list object with two data frames, `cps_school_year$school_year` and `cps_school_year$days_off`.
- `cps_address`: contains lat/lon coordinates and full addresses as understood by the google maps API.
- `cps_security_personnel`
- `cps_crosswalk`: this file helps link the `cps_security_personnel` data with the all other data sources by merging on the `unit_number` variable.
- `cpd_crime_codes`: contains crime codes from the Chicago PD (IUCR codes) and the FBI. it is a list of two data frames, `cpd_crime_codes$iucr` and `cpd_crime_codes$fbi`.


## Example: `cps_address` dataset

```{r cps-address, warning=FALSE, message=FALSE, echo=TRUE, eval=TRUE}
# first 10 full school address for academic year 2009 - 2010
cps_address %>% 
  dplyr::filter(school_year == 2010) %>%
  dplyr::select(schoolname, school_year, address_full, lat, lon) %>%
  head(10)
```

# Other Info

In the [package directory `data-raw`](https://github.com/dantonnoriega/sppedr/tree/master/data-raw), there is a `README.txt` file that explains where all the internal datasets come from and/or how they are built. Scripts that build most of these data are also in `data-raw`. Note that this directory is accessible via the github repo, not the package itself.

# Functions

The only function that one really needs call is `get_cpd_crime()`. This is because these data are much larger and could not be included as part of the package. It will import these data from the `main_dir` set using the `set_main_dir()` function.

The following functions do not need to be called *unless you want to regenerate these data again from scratch*.

- `get_cps_2008_2016()`
- `get_cps_address()`
- `get_cps_security_personnel()`

To do so, you need to set `force = TRUE`. Otherwise, the function will just load the package version. *I would recommend NOT to use the force option*.


## Example

Here is an example where the CPS security personnel data is spread and the merged to the crosswalk data.

```{r example, warning=FALSE, message=FALSE, echo=TRUE, eval=TRUE}

personnel_wide <- cps_security_personnel %>%
  dplyr::left_join(., cps_crosswalk, by = 'unit_number') %>%
  dplyr::mutate(job_description = gsub('school ', '', job_description)) %>%
  dplyr::mutate(job_description = gsub('[[:space:]]', '_', job_description)) %>%
  dplyr::filter(!is.na(schoolidr_c_d_t_s)) %>%
  tidyr::spread(job_description, n) %>%
  dplyr::mutate_if(is.integer, dplyr::funs(replace(., is.na(.), 0))) %>% # replace NAs with 0
  dplyr::select(-unit_number, -abbreviated_name) %>%
  dplyr::mutate(school_year = as.integer(school_year))

# list first 10 security_officer counts
personnel_wide %>%
  dplyr::select(school_year, school_name, security_officer) %>%
  head(10)

```

